Tables

### 2023-10-27 output/paper/tables.qmd
Kept working on functions to process results. Now table 1 for paper and cleaned previous results.

- Begin each table on a new page after the list of references.
- Tables may not contain parts.
- Provide the title for each table above the table and the notes below the table.
- List footnotes after the general one, one per line and indicated with a lowercase italicized letter.

>>>>

- Begin each table on a new page after the list of references, numbered with Arabic numerals.
- Leave blank spaces for no entry.
- Tables may not contain parts.
- Provide the title for each table above the table and the notes below the table.
- Order footnotes: abbreviations listed alphabetically and separated by semicolons; others preceded by superscript lowercase letter.
